Recpature distances

### 2025-01-22 recaptureanalysis/recaps.Rmd
Tweaks to biomass and updates to recapture analyssi.

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
load("Recaps2.RData")
save( distances, recaps, recaps2, recaps3,  distances2, alldist, alldist2, alldist2.1, releasestat,
      turbdat_ave, file = "Recaps2.RData")
```

@@

recaps = read_excel("data/Running Delta Smelt Catch.xlsx", 
                    sheet = "Delta Smelt Catch Data") %>%
  rename( Latitude= `LatitudeStart`, Longitude = `LongitudeStart`)

recaps = recaps %>%
  mutate(FishID = paste("Fish", 1:nrow(recaps))) %>%
  select(-ReleaseDate, -Preservation, -Disposition, -SpecialStudyID, -MarkCode, -Dateknown)

@@

#now let's do Rio Vista hard
RVhard = filter(recaps2,  Site == "Rio Vista", !is.na(Latitude))
rvh = filter(release, Site == "Rio Vista", Type == "Hard (trailer)") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
  distinct()
tesst3 = GGdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = rvh)

>>>>

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
library(tidyverse)
library(readxl)
library(sf)
library(lubridate)
library(spacetools)
library(deltamapr)
# load("Recaps2.RData")
# save( distances, recaps, recaps2, recaps3,  distances2, alldist, alldist2, alldist2.1, releasestat,
#       turbdat_ave, file = "Recaps2.RData")
```

@@

recaps = read_excel("data/Running Delta Smelt Catch_2023-09-05.xlsx", 
                    sheet = "Delta Smelt Catch Data") %>%
  rename( Latitude= `LatitudeStart`, Longitude = `LongitudeStart`)

recaps = recaps %>%
  mutate(FishID = paste("Fish", 1:nrow(recaps))) %>%
  select(-ReleaseDate, -Preservation, -Disposition, -SpecialStudyID, -MarkCode)

@@

#now let's do Rio Vista hard
RVhard = filter(recaps2,  Site == "Rio Vista", !is.na(Latitude))
rvh = filter(release, Site == "Rio Vista",  Type == "Hard (large scale)") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
  distinct()
tesst3 = GGdist(Water_map = spacetools::Delta, Points = RVhard, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = rvh)

#Sandy Beach
sandyhard = filter(recaps2,  Site == "Sandy Beach", !is.na(Latitude))
svh = filter(release, Site == "Sandy Beach") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
  distinct()
tesst4 = GGdist(Water_map = spacetools::Delta, Points = sandyhard, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = svh)

#lookout
lookout = filter(recaps2,  Site == "Lookout Slough", !is.na(Latitude))
los = filter(release, Site == "Lookout Slough") %>%
  select(LatitudeR, LongitudeR)%>%
  rename(Latitude = LatitudeR, Longitude = LongitudeR) %>%
  distinct()
tesst5 = GGdist(Water_map = spacetools::Delta, Points = lookout, Latitude_column = `Latitude`,
                Longitude_column = `Longitude`, PointID_column = FishID, EndPoint = los)
